---
title: "Automatic cell-type annotation"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Automatic cell-type annotation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  tidy = FALSE,
  message = FALSE,
  # error = FALSE,
  warning = FALSE,
  eval = FALSE,
  fig.align = "center"
)
options(width = 80)
```

**scPlant** have implemented several different solutions for automatic cell-type annotation that are based on popular tools, including [SingleR](https://doi.org/10.1038/s41590-018-0276-y), [Garnett](https://doi.org/10.1038/s41592-019-0535-3), [scCATCH](https://doi.org/10.1016/j.isci.2020.100882), [Celaref](https://www.bioconductor.org/packages/release/bioc/html/celaref.html) and [CellAssign](https://doi.org/10.1038/s41592-019-0529-1).

```{r}
library(scPlant)
```

## Reference based tools

`SingleR`, `Celaref` and `CellFunTopic` need reference data to perform automatic cell-type annotation.

```{r}
SeuratObj <- AutoAnnotate_SingleR(SeuratObj, ref, ref_type = "single-cell")
```

```{r}
result <- AutoAnnotate_Celaref(SeuratObj, counts_ref, cellinfo_ref)
```

```{r}
result <- CellFunTopic::predictFun(SeuratObj, reference_SeuratObj)
```


## Marker based tools

`scCATCH`, `Garnett` and `CellAssign` need marker genes to perform automatic cell-type annotation.

Please view the help document of these functions for the required format of marker genes, such as `?AutoAnnotate_scCATCH`.

```{r}
result <- AutoAnnotate_scCATCH(SeuratObj, marker_custom)
```

```{r}
SeuratObj <- AutoAnnotate_Garnett(SeuratObj, marker_file_path, gene_id_type, species = 'Ath')
```

```{r}
SeuratObj <- AutoAnnotate_CellAssign(SeuratObj, marker_list)
```



