---
title: "Functional annotation"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Functional annotation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  tidy = FALSE,
  message = FALSE,
  # error = FALSE,
  # eval = F,
  warning = FALSE,
  fig.align = "center"
)
options(width = 80)
```


**scPlant** provides methods for Gene Set Enrichment Analysis (GSEA) in model plants. We recommend [CellFunTopic](https://github.com/compbioNJU/CellFunTopic) package to visualize the GSEA result and perform topic modelling, revealing cellular programs shared across cell types or exclusive to a particular cell type.

We provide a real scRNA-seq data of Arabidopsis thaliana ([Zhang et al., 2019](https://www.sciencedirect.com/science/article/pii/S1674205219301339)) as example data, download [here](https://figshare.com/articles/dataset/Auxiliary_data_and_codes_for_scPlant/23498402)


```{r, echo = FALSE}
SeuratObj <- readRDS(file = "../vignette_data/ath.rds")
```


## Gene Set Enrichment Analysis (GSEA)

```{r, eval=FALSE}
library(scPlant)
SeuratObj <- RunGSEA_plant(SeuratObj, by = 'GO', GeneIDtype = 'TAIR', minpct = 0.25)
```

#### Visualize the GSEA result

Refer to https://compbioNJU.github.io/CellFunTopic for more visualization of GSEA result.

```{r, fig.height=10, fig.width=10}
library(CellFunTopic)
pathway_unique_shared(SeuratObj, by = "GO", fontsize_row = 4, scale = "row")
hierarchyplot_tree(SeuratObj, by = "GO", topaths = 4, cluster_cutree_k = 14, pathway_cutree_k = 14,
                   vertex.label.cex=0.5, edge.max.width=1, vertex.size.cex=0.7)
```


## Topic modelling

```{r, eval=FALSE}
SeuratObj <- runLDA(SeuratObj, k = 23)
```

#### Visualize the topic modelling result

Refer to https://compbioNJU.github.io/CellFunTopic for more visualization of topic modelling result.

```{r}
ldaOut <- SeuratObj@misc$ldaOut
betaDF <- tidytext::tidy(ldaOut, matrix = "beta")
pws <- ID2Description(SeuratObj, by = "GO")
betaDF <- dplyr::mutate(betaDF, descrip=unname(pws[term]))
gammaDF <- tidytext::tidy(ldaOut, matrix = "gamma")
```

```{r}
cluster_topic_hmp(ldaOut)
plot_sankey(gammaDF, topn=1, plotHeight = 600)
```

```{r, fig.height=10, fig.width=10}
topicNW3(betaDF, topn=10, pws = pws)
```

```{r}
topicProb(SeuratObj, topic=21, pointSize=0.1) + Seurat::NoAxes()
Topterms_Topic(betaDF, Topic = 21, topn = 20)
```

```{r, fig.height=10, fig.width=10}
cosine_network_term(SeuratObj, radius = 0.2)
```



