---
title: "Cross-species integration"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Cross-species integration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  tidy = FALSE,
  message = FALSE,
  # error = FALSE,
  # eval = F,
  warning = FALSE,
  fig.align = "center"
)
# options(width = 80)
```


We have provided tools in the **scPlant** framework for cross-species integration of single-cell data in matched organs/tissues using one-by-one orthologous genes as anchors. Note that scPlant mainly uses the strategy of canonical correlation analysis (CCA) and reciprocal PCA (RPCA) for data integration as described in [Stuart\*, Butler\* et al, 2019](https://www.cell.com/cell/fulltext/S0092-8674(19)30559-8). What's more, scPlant normalizes each dataset with SCTransform ([Hafemeister and Satija, 2019](https://genomebiology.biomedcentral.com/articles/10.1186/s13059-019-1874-1)) before integration.

```{r}
library(scPlant)
```

Here, we take 3 toy example data (expression matrix) to demonstrate how to perform a cross-species integration.

```{r}
dim(example_Ath) # toy example data of Arabidopsis thaliana
dim(example_Osa) # toy example data of Oryza sativa
dim(example_Zma) # toy example data of Zea mays
```


## Cross-species integration

Multiple expression matrices can be provided, as long as the parameter `species` is specified.

```{r, eval = FALSE}
integratedObj <- crossSpecies_integrate(matrices = list(example_Ath, example_Osa, example_Zma), 
                                        species = c('Ath', 'Osa', 'Zma'), resolution = 0.5)
```


```{r, echo = FALSE}
integratedObj <- readRDS(file = "../vignette_data/integratedObj.rds")
```

We finally got an integrated Seurat object `integratedObj`, which we can perform downstream analysis on.

```{r}
Seurat::DefaultAssay(integratedObj) <- 'SCT'
dim(integratedObj)
```


## Visualize integration result

```{r}
Seurat::DimPlot(integratedObj, reduction = "umap", group.by = "species") + Seurat::NoAxes()
```

```{r, fig.height=5, fig.width=10}
Seurat::DimPlot(integratedObj, reduction = "umap", group.by = "seurat_clusters", label = F,
                repel = TRUE, split.by = "species") + Seurat::NoAxes()
```

Bar plot showing the percentage of cells from different species:

```{r}
species_percentage(integratedObj, group_by = 'seurat_clusters')
```




