---
title: "Pre-processing"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pre-processing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  tidy = FALSE,
  message = FALSE,
  # error = FALSE,
  warning = FALSE,
  eval = FALSE,
  fig.align = "center"
)
options(width = 80)
```


We recommend **CellFunTopic** package to perform data pre-processing for convenience. The **CellFunTopic** package provides a convenient workflow for data pre-processing (quality control, normalization, dimension reduction, clustering, differential expression analysis, etc.) by integrating methods of `Seurat` package.

```{r}
devtools::install_github("compbioNJU/CellFunTopic")
library(CellFunTopic)
```


## Load in the data

CellFunTopic allows various types of input, including CellRanger outputs, raw gene expression matrix, and popular R objects used for single cell analysis such as `SingleCellExperiment`, `Seurat`, `CellDataSet`. CellFunTopic will transform different input data into a `Seurat` object.

Let us use a randomly generated tiny single-cell expression matrix of Arabidopsis thaliana as a toy example. 

```{r}
dim(example_Ath) # an internal example data of scPlant 
SeuratObj <- readData(data = example_Ath, type = 'expMatrix', species = "Arabidopsis thaliana")
```

You can also take CellRanger outputs as input:

```{r}
SeuratObj <- readData(data = "filtered_gene_bc_matrices/TAIR/", type = '10X', species = "Arabidopsis thaliana")
```


## Standard pre-processing workflow

Then we can perform pre-processing conveniently. If users provide a pre-processed data, this step can be skipped.

```{r}
SeuratObj <- QCfun(SeuratObj)
SeuratObj <- RunSeurat(SeuratObj, nPCs = 10, resolution = 1)
unique(Seurat::Idents(SeuratObj)) # see how many clusters we got.
```









