---
title: "Pseudotime trajectory inference"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pseudotime trajectory inference}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  tidy = FALSE,
  message = FALSE,
  # error = FALSE,
  eval = FALSE,
  warning = FALSE,
  fig.align = "center"
)
options(width = 80)
```

**scPlant** offers convenient implementation of pseudotime trajectory inference by incorporating two public tools, Monocle and Slingshot.


```{r}
library(scPlant)
```

### Monolce2

If `save_plot = TRUE`, output plots will be stored in `./output/RunMonocle2`.

```{r}
result <- RunMonocle2(SeuratObj, save_plot = TRUE)
```

### Monolce3

If `save_plot = TRUE`, output plots will be stored in `./output/RunMonocle3`.

```{r}
result <- RunMonocle3(SeuratObj, save_plot = TRUE)
```


### Slingshot

If `save_plot = TRUE`, output plots will be stored in `./output/RunSlingshot`.

```{r}
result <- RunSlingshot(SeuratObj, save_plot = TRUE)
```

### CytoTRACE

If `save_plot = TRUE`, output plots will be stored in `./output/CytoTRACEoutput`.

```{r}
result <- RunCytoTRACE(SeuratObj, save_plot = TRUE)
```




