---
title: "Gene regulatory network construction"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Gene regulatory network construction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  tidy = FALSE,
  message = FALSE,
  # error = FALSE,
  warning = FALSE,
  fig.align = "center"
)
options(width = 80)
```

Gene regulatory networks (GRNs), consisting of the interaction between transcription factors (TFs) and their target genes, orchestrate cell-specific gene expression patterns and in turn determine the function of the cell. To construct cell-type specific GRNs using single-cell data, we have incorporated the widely used single-cell GRN analysis tool SCENIC ([Aibar et al., 2017](https://www.nature.com/articles/nmeth.4463)) into the scPlant pipeline, and prepared required cis-Target databases in order to support SCENIC for data analysis in plants. What's more, we have provided various visualization tools to display single-cell GRN results in different ways. Three plant species (Arabidopsis thaliana, Oryza sativa, Zea mays) are supported for now, and more plant species will be supported soon.

```{r, eval = FALSE}
library(scPlant)
```




